% INTENTIONALLY FLAWED DEMO PAPER FOR CITATION-CHECKER TESTING
\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{hyperref}
\title{Mini Demo Paper: (Intentionally) Messy Citations}
\author{Test Author}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
Expansive, informative datasets are vital foundations for research across many fields.
Assembling grand datasets often poses difficulty for authors and stakeholders throughout the lifecycle,
yet we outline a succinct framework of important elements to consider when forging a dataset of your own. % <- near-duplicate phrasing (no citation)
We also touch on top-down, bottom-up, and hybrid approaches to AI morality with a brief focus on reinforcement learning and principles. % <- mirrors second paper (no/weak citation)
\end{abstract}

\section{Introduction}
With the progression of member states to openly publish administrative data, the opportunity to move beyond local-scale studies has advanced with expansive, collaborative, multi-national datasets.% <- mirrors EuroCrops intro (no citation)
While there are clear advantages of a large and diverse dataset, legacy and manual systems make gathering data at scale an ever-laborious task. % <- mirrors EuroCrops (no citation)

\textbf{Potential issues baked in here:}
\begin{itemize}
  \item Unattributed reuse / close paraphrase of published text (this section).
  \item Irrelevant or incorrect citations to the wrong source (e.g., \cite{Eurocrops2021} about AI ethics).
  \item Dangling citation keys (e.g., \cite{NonExistingKey}).
\end{itemize}

\section{Six Challenges in Transnational Datasets}
We identify six challenges when compiling collaborative, transnational datasets:\footnote{Terms listed without proper source on purpose.}
\emph{discoverability, accessibility, homogeneity, scalability, distributability, maintainability}. % <- exact list reused, no citation

Even when authorities provide data, platforms may require registration and language barriers persist. % <- mirrors phrasing
Formats vary (e.g., shapefiles vs geopackages), further impeding research at scale. % <- mirrors phrasing

\paragraph{(Irrelevant citation)} As ethics principles illustrate tensions like fairness and transparency \cite{Eurocrops2021}, % <- cites the wrong paper on purpose
stakeholders should be notified centrally of updates.\footnote{This sentence mixes topics to bait a checker.}

\section{Top-Down, Bottom-Up, and Hybrid Ethics in AI}
Top-down AI ethics can be seen as rule-based systems driven by authorities or philosophical doctrines, whereas bottom-up ethics learn from data and experience (e.g., reinforcement learning).
Hybrid methods mix both, sometimes combining programmed constraints with learned behavior. % <- mirrors second paper
It has been argued that ``an ethical algorithm is a contradiction in terms.'' % <- unattributed quote intentionally (from a source cited in the ethics paper)
Moreover, political angles matter when corporate or governmental powers impose principles that sound good but are too broad to be action-guiding.\cite{RobertsMontoyaWrongYear} % <- wrong-year/metadata key

\paragraph{(Misdirected citation)} For a European agricultural case study, see \cite{RobertsMontoya2022}. % <- cites ethics paper for crops case (irrelevant)

\section{Method Sketch}
We segment paragraphs, fingerprint text, embed sentences, and run cross-encoder reranking.
Uncited claims about exact procedures and thresholds are left vague by design to trigger ``needs-citation'' warnings.

\section{Conclusion}
We have distilled challenges and opportunities for large, interwoven datasets and reflected on AI morality across theoretical, technical, and political lenses.
There is no single correct way to make AI ethical; care must be taken at every turn to right wrongs in the digital age. % <- mirrors second paper conclusion (no citation)

% ------------------ INTENTIONALLY BAD BIBLIOGRAPHY ------------------
\begin{thebibliography}{9}

\bibitem{Eurocrops2021}
M.~Schneider, C.~Marchington, and M.~Koerner.
\newblock Challenges and Opportunities of Large Transnational Datasets: A Case Study on European Administrative Crop Data.
\newblock \emph{arXiv}, 2021. % <- wrong year on purpose (should be 2022)
\newblock DOI: \href{https://doi.org/10.0000/fake-doi}{10.0000/fake-doi} % <- fake DOI

\bibitem{Eurocrops2021-dup}
M.~Schneider, C.~Marchington, and M.~Körner.
\newblock EuroCrops: A pan-european dataset for time series crop type classification.
\newblock In \emph{Big Data from Space}, 2021.
% <- duplicate/near-duplicate and not the same paper; also casing differences; used to trigger duplicate/irrelevant linkages.

\bibitem{RobertsMontoyaWrongYear}
J.~S.~Roberts and L.~N.~Montoya.
\newblock Contextualizing Artificially Intelligent Morality: A Meta-Ethnography of Theoretical, Political and Applied Ethics.
\newblock \emph{arXiv}, 2024. % <- wrong year on purpose

\bibitem{RobertsMontoya2022}
J.~S.~Roberts and L.~N.~Montoya.
\newblock Contextualizing Artificially Intelligent Morality: A Meta-Ethnography of Top-Down, Bottom-Up, and Hybrid Models.
\newblock \emph{Working Paper}. Available at: \url{http://example.com/bad-url} % <- bad/irrelevant URL
% <- Irrelevant use earlier and two inconsistent titles for the same work.

\bibitem{UnusedEntry}
A.~Author.
\newblock Unused Reference to Trigger ``unused bibliography entry''.
\newblock Some Venue, 2019. % <- never cited in text

\end{thebibliography}

% Notes for your checker:
% - Missing actual citations for paraphrased EuroCrops material (Intro; Section 2).
% - Unattributed quote in ethics section.
% - Wrong-year metadata and inconsistent titles for the ethics paper.
% - Irrelevant/misdirected citations (EuroCrops cited for ethics; ethics cited for crops).
% - Dangling key: \cite{NonExistingKey} above has no \bibitem.
% - Duplicate-ish entry for EuroCrops; fake DOI; bad URL; unused bibliography entry.

\end{document}
